Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2023-05-12 noise_covid_v2.Rmd
prepare draft
source scripts within Rmd file to produce first draft

---
title: Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model
author: "Rachael Aber"
header-includes: \usepackage{setspace}\doublespacing
output:
  html_document:
    df_print: paged
  pdf_document: default
geometry: margin=2.54cm
fontsize: 12pt
---

@@

For this project, we use county-level COVID-19 incidence data. Source: [USAFacts](https://usafacts.org/). The data is weekly case counts by US county.

Approximately one month of data on either side of November 24th, 2020 was used in the analysis. This step was done to include a set number of "waves" of incidence in the model fit to each side of the hypothesized change. However, we acknowledge that there is a trade-off between including few waves and increasing the power of the proposed test by including more time series data.

@@

```{r}
rat <- data.frame(Mean = c(5, 10), Ratio = c(2.236068, 3.162278))
kable(rat, align = "cc", caption = "Poisson mean to standard deviation ratio", digits=2)
```

@@

```{r, fig.cap="Average Pothoff-Whittinghill (PW) statistic for each NY county plotted against county population size."}

library(tidyverse)
library(changepoint)

@@

ch_pts <- map(scaled_cases, ~ cpt.mean(., class = TRUE, penalty = "MBIC", pen.value = 0, method = "PELT", param.estimates = TRUE))

segments <- map2(.x = ny_df_t$DailyNewConfirmedCases[-c(2, 8, 21, 49, 54, 62)], .y = ny_df_t$ch_pts[-c(2, 8, 21, 49, 54, 62)], ~ get_segments(series = .x, changepoints = .y))

@@

plot(log(ny_df_t$populations[-c(2, 8, 21, 49, 54, 62)]), log(unlist(mean_pw)), xlab="Log Population Size", ylab=" Log Mean PW Statistic", col=2)
```

Methods designed specifically for count data show a similar dependence on population size. The cpt.meanvar function (changepoint package) is designed to detect changes in mean and variance in count data. The number of changepoints identified for a time series increases with its population size.

@@

ny_df_t$ch_pts2 <- map(as.data.frame(new_cases_subset), ~ cpts(cpt.meanvar(., class = TRUE, penalty = "MBIC", pen.value = 30, method = "PELT", test.stat = "Poisson", param.estimates = TRUE, minseglen = 2))) 
ny_df_t$n_ch_pts2 <- map(ny_df_t$ch_pts2, ~length(unlist(.)))

plot(log(ny_df_t$populations), log(unlist(ny_df_t$n_ch_pts2)), xlab="Log Population Size", ylab=" Log Number of Changepoints", col=2)
```

## Modeling proccess mean

We propose a generalized linear model (GLM) approach to quantify incidence dispersion in segments of a time series, using a single parameter, $\theta$, while separately accounting for population size in the model. Another approach is to fit one model to the entire time series accounting for autocorrelation using a quasi-likelihood approach using a specified matrix V (Barron 1992). We account for unobserved heterogeneity, contagion, and time dependence in rate through specifying a changing process mean (to account for autocorrelation) and specifying a overdispersed conditional distribution (to account for overdispersion).

A recently proposed negative binomial regression model for time series of counts also accommodates serial dependence (Davis and Wu 2009). The approach presented here is similar, but we use a linear predictor, $\eta$, that includes a generalized additive model (GAM) with one explanatory variable, time. In the GAM framework, the function for a predictor can be represented using spline functions:

 $$g(E[Y_i]) = f(t_i) = \sum_m^M\beta_m h_m(t_i)$$
 $$log(E[Y_i]/n_i) = \sum_m^M\beta_m h_m(t_i)$$

Natural splines are cubic splines which are linear outside of the boundary knots (Perperoglou et al. 2019). The degrees of freedom were chosen due to **

$$g(E[Y_i]) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$
$$log(E[Y_i]/n_i) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$
```{r, fig.cap="County case count time series for each New York county with the hypothesized Thanksgiving changepoint represented by the black vertical line (L), and total New York COVID-19 case count time series (R)."}

inds <- seq(start_date, end_date, by = "day")

plot(new_cases_subset[state_index[1],], type = "l", xaxt = "n", ylab = "Daily Incidence", xlab = "Date")
for (i in 2:length(state_index)){
  lines(new_cases_subset[state_index[i],], col=sample(rainbow(10)))
}
abline(v=inds[30], lwd=2)
axis(1, inds, inds, cex.axis = .7)

ny_col_sum <- matrix(unlist(ny_df_t$DailyNewConfirmedCases), nrow=62,
                     ncol=length(ny_df_t$DailyNewConfirmedCases[[1]]))
ny_cases <- colSums(ny_col_sum)
plot(ny_cases ~ inds, type="l", col=6, xlab="Date", ylab="Daily Incidence")
abline(v=inds[30], lwd=2)
```

```{r, fig.cap="County case count time series for each Florida county with the hypothesized Thanksgiving changepoint represented by the black vertical line (L), and total Florida COVID-19 case count time series (R)."}

par(mfrow=c(1,2))
# By visual inspection 
plot(fl_df_t$DailyNewConfirmedCases[[1]] ~ inds, type="l", ylim=c(0, 5000), xaxt="n", ylab="Daily Incidence", xlab="Date")
for (i in 2:dim(fl_df_t)[1]){
  lines(fl_df_t$DailyNewConfirmedCases[[i]] ~ inds, col=sample(rainbow(10)))
}
abline(v=inds[30], lwd=2)
axis(1, inds, inds, cex.axis = .7)

fl_col_sum <- matrix(unlist(fl_df_t$DailyNewConfirmedCases), nrow=62,
                     ncol=length(fl_df_t$DailyNewConfirmedCases[[1]]))
fl_cases <- colSums(fl_col_sum)
plot(fl_cases ~ inds, type="l", col=6, xlab="Date", ylab="Daily Incidence")
abline(v=inds[30], lwd=2)
```
## IRLS

Briefly, what iteratively reweighted least squares (IRLS) does is compute an adjusted dependent variable, compute a weight matrix, and compute (using weighted least squares) coefficients and therefore the linear predictor as well.

In irls.nb.1 in the NBPSeq R package (*cite):

1. Initial mu (either supplied or computed) and eta = log(mu/s).
2. z = eta - offset + (y - mu)/mu
3. w = drop(\mu/sqrt(varmu))
4. call Fortran code to perform weighted LS. Weighted least squares produces: $\hat{\beta} = (X^TWX)^{-1}X^TWY$, where weight is based on the variance of the observation. 
5. Then new values of mu and eta from new coefficients.

Within diy_spl_fit, fit.nb.regression is run and the standard error of param theta is computed by inverting info matrix, take [1,1] entry and take square root. Within fit.nb.regression, kappa is optimized, then irls.nb.1 (the IRLS portion) is called, then additional output - like the information matrix - is added.

@@

Note that if the offset model were perfect, the estimated coefficient on log population would be exactly one:
$$log(E[Y_i]/n_i) = \sum_m^M\beta_m h_m(t_i)$$
, where $n_i$ is the population size, $Y_i$ is incidence, and $t_i$ is the time point.

In this case, a log link function is used:

  $$log(E[Y_i])-log(n_i) = \sum_m^M\beta_m h_m(t_i)$$
  $$log(E[Y_i]) =  \sum_m^M\beta_m h_m(t_i) + log(n_i)$$

@@

```{r}
disp_stats <- c()
for (i in 1:dim(ny_fl_df_t)[1]){
  Y <- ny_fl_df_t$DailyNewConfirmedCases[[i]]
  spline_mod.1.pois <- spl_fit_pois(Y = Y, population=ny_fl_df_t$populations[i], inds=1:(length(Y)/2))
  disp_stats <- c(disp_stats, spline_mod.1.pois$deviance/spline_mod.1.pois$df.residual)
  #print(summary(spline_mod.1.nb)$coefficients[,4])
}
```

@@

```{r, fig.cap="Average squared residual per bin v. fitted bin mean for Poisson model (L) and negative binomial model (R) with number of bins = 25 (observations per bin = 11). Visualizations displayed for a randomly chosen counties"}
par(mfrow=c(1,2))
i <- 2
Y <- ny_fl_df_t$DailyNewConfirmedCases[[i]]
spline_mod.1.pois <- spl_fit_pois(Y = Y, population=ny_fl_df_t$populations[i], inds=1:(length(Y)/2))
spline_mod.1.nb <- diy_spl_fit(Y = Y, population=ny_fl_df_t$populations[i], inds=1:(length(Y)/2), df = 3)
bin_it(fits=spline_mod.1.pois$fitted.values, y=Y[1:(length(Y)/2)], nbins=25)
abline(0,1)
abline(0,2, col=3)
bin_it(fits=spline_mod.1.nb$mu, y=Y[1:(length(Y)/2)], nbins=25)
abline(0,1)
abline(0, 2, col=3)

```

To identify an appropriate conditional distribution, the value of Poisson model residual deviance (D) divided by its degrees of freedom (df) was used to verify that overdispersion at the time point level is present under this model and found that only `r sum(disp_stats <=1)` dispersion statistics were less than or equal to one. Since residual deviance of a model is expected to be asymptotically distributed as $\chi^2_{df}$, where the degrees of freedom are the number of observations minus the number of estimated parameters, an indication that a model may be underestimating dispersion (that the data is inconsistent with the model) is that D/df >> 1.

@@

```{r, fig.cap="Poisson and negative binomial fits to incidence data prior to Thanksgiving 2020 in a single county time series."}

source("code/check_nb_estimation.R")
```

@@

```{r, fig.cap="Example of empirical increase in dispersion at the hypothesized Thanksgiving 2020 changepoint."}
plot(ny_df_t$DailyNewConfirmedCases[[14]] ~ inds, xaxt="n", ylab="Daily Incidence", xlab="Date")
abline(v=inds[30], col=2)
axis(1, inds, inds, cex.axis = .7)
```

We tested the hypothesis that the incidence dispersion parameter decreases at the Thanksgiving changepoint of interest: $\theta_1 > \theta_2$. Hypothesis tests were conducted to assess whether $\theta$ is smaller (more variable incidence) after Thanksgiving 2020. The Wald test is used, where the estimates of $\theta$ in different segments are considered independent. This approach is possible because we use maximum likelihood estimates of $\theta$ (found by alternating between fitting a GLM for a given theta and then (for fixed means) estimating $\theta$). The standard error of $\theta$ is found utilizing the observed information (Venables and Ripley 2002).

@@

## Thanksgiving 2020: New York and Florida

First, for every county, the model was fit separately to either side of November 25th, 2020 - where the 25th was included in the second segment -  in order to compute values of $\hat{\theta_1}$ and $\hat{\theta_2}$. A test of the one-sided upper alternative that the difference between before and after is positive (lower theta after Thanksgiving) was performed.

```{r, fig.cap = "P-values resulting from testing whether the dispersion parameter is smaller after Thanksgiving in each county in New York and Florida."}

# Wald test for NY Thanksgiving in 2020 - doesn't converge for 13th and 50th NY counties
diff_thetas <- c()
t_ps <- c()
for (i in 1:dim(ny_df_t)[1]){ 
  if (i == 13 | i ==50){
    p = NA
    theta = NA
  }
  else{
    p <- W(y=ny_df_t$DailyNewConfirmedCases[[i]], pop=ny_df_t$populations[i], split=30)
    theta1 <- diy_spl_fit(Y=ny_df_t$DailyNewConfirmedCases[[i]], population =
                            ny_df_t$populations[i],
                          inds=1:(length(ny_df_t$DailyNewConfirmedCases[[i]])/2), df = 3)$theta
    theta2 <- diy_spl_fit(Y=ny_df_t$DailyNewConfirmedCases[[i]], population =
                            ny_df_t$populations[i],
                          inds=(length(ny_df_t$DailyNewConfirmedCases[[i]])/2
                                +1):length(ny_df_t$DailyNewConfirmedCases[[i]]), df = 3)$theta
  }
  t_ps <- c(t_ps, p)
  diff_thetas <- c(diff_thetas, abs(theta1 - theta2))
}
ny_df_t$p <- t_ps
ny_df_t$diff_thetas <- diff_thetas

# Wald test for FL Thanksgiving in 2020
diff_thetas <- c()
t_ps <- c()
for (i in 1:dim(fl_df_t)[1]){ 
  p <- W(y=fl_df_t$DailyNewConfirmedCases[[i]], pop=fl_df_t$populations[i], split=30)
  theta1 <- diy_spl_fit(Y=fl_df_t$DailyNewConfirmedCases[[i]], population = fl_df_t$populations[i],
                       inds=1:(length(fl_df_t$DailyNewConfirmedCases[[i]])/2), df = 3)$theta
  theta2 <- diy_spl_fit(Y=fl_df_t$DailyNewConfirmedCases[[i]], population = fl_df_t$populations[i],
                       inds=(length(fl_df_t$DailyNewConfirmedCases[[i]])/2 +
                               1):length(fl_df_t$DailyNewConfirmedCases[[i]]), df = 3)$theta
  t_ps <- c(t_ps, p)
  diff_thetas <- c(diff_thetas, abs(theta1-theta2))
}
fl_df_t$p <- t_ps
fl_df_t$diff_thetas <- diff_thetas

#p_adj_t <- p.adjust(t_ps, method = "BH")
par(mfrow=c(2,2))
# Histogram of p-values NY
hist(ny_df_t$p, col=2, breaks=20, xlab="p-values", main=NULL)
# Power lower based on population? NY
plot(ny_df_t$p ~ ny_df_t$populations)
# Histogram of p-values FL
hist(fl_df_t$p, col=2, breaks=20, xlab="p-values", main=NULL)
# Power lower based on population? FL
plot(fl_df_t$p ~ fl_df_t$populations)

```

```{r, fig.width=7, fig.height=7}
# Plot fitted curves for the counties with significant p-values

ny_indeces <- which(ny_df_t$p < 0.05)

par(mar=c(1,1,1,1))
par(mfrow=c(6,2))

for (i in ny_indeces){

mu <- diy_spl_fit(Y = ny_df_t$DailyNewConfirmedCases[[i]], population = ny_df_t$populations[i], inds=1:length(ny_df_t$DailyNewConfirmedCases[[i]]), df = 3)$mu

plot(1:length(ny_df_t$DailyNewConfirmedCases[[i]]), ny_df_t$DailyNewConfirmedCases[[i]], ylim=c(0,500))
lines(mu, col=2)
}

fl_indeces <- which(fl_df_t$p < 0.05)

par(mar=c(1,1,1,1))
par(mfrow=c(6,2))

for (i in fl_indeces){

mu <- diy_spl_fit(Y = fl_df_t$DailyNewConfirmedCases[[i]], population = fl_df_t$populations[i], inds=1:length(fl_df_t$DailyNewConfirmedCases[[i]]), df = 3)$mu

plot(1:length(fl_df_t$DailyNewConfirmedCases[[i]]), fl_df_t$DailyNewConfirmedCases[[i]])
lines(mu, col=2)
}

```
https://cran.r-project.org/web/packages/tigris/readme/README.html

```{r, echo=F, fig.cap="P-values for each New York county resulting from the test of the one-sided upper alternative that time series dispersion is greater after Thanksgiving 2020"}

ny <- counties("New York")

p <- round(ny_df_t$p, digits=1)
p[is.na(p)] <- "na"
ny$p <- p

ggplot(ny) +
  geom_sf(aes(fill = p))

fl <- counties("Florida")

p <- round(fl_df_t$p, digits=1)
p[is.na(p)] <- "na"
fl$p <- p

ggplot(fl) +
  geom_sf(aes(fill=p))

```
# Simulation

## Validity of the hypothesis test

@@

```{r, fig.cap = "Representative epidemic curve to inform the validity simulation and the power simulation."}

curve_parms <- data.frame(n = rep(mean(ny_df_t$populations), times = 300),  b = rep(30, times = 300), c = rep(200, times = 300), theta1 = c(seq(4, 10, length=100), seq(4, 10, length=100), seq(9, 3, length=100)), theta2 = c(seq(4, 10, length=100), seq(12, 6, length=100), seq(2, 8, length=100)))

plot(1:60, u_t(n = curve_parms$n[1], t = 1:60, b = curve_parms$b[1], c=curve_parms$c[1]), ylim = c(0, 1000))
```

```{r, fig.cap="Validity simulation p-values."}
# Wald test for simulated data - same process as was done to real time series from NY counties

splits <- c(20, 30, 40)

p_vals <- c()
diff_vals <- c()

for (k in splits){
  for (i in 1:100){

  sides <- rerun(sim_sides(parms=curve_parms[i,], time=1:60), .n=10)
  ps <- map(sides, ~ W(y=., pop=curve_parms$n[i], split=k, verbose=FALSE))

  p_vals <- c(p_vals, ps)
  diff_vals <-c(diff_vals, rep(abs(curve_parms[i,4]-curve_parms[i,5]), times=10))

  }
}

hist(unlist(p_vals), col=2, breaks=20, xlab="p-values", main=NULL)

```

## Power of the hypothesis test

@@

```{r, fig.cap="Power simulation p-values."}
p_pows <- c()
diff_pows <- c()

for (k in splits){
  for (i in 100:300){ # change to 100:300 for two-sided hyp test

    sides <- rerun(sim_sides(parms = curve_parms[i,], time=1:60), .n=10)
    ps <- map(sides, ~ W(y=., pop=curve_parms$n[i], split=k, verbose=FALSE))

    p_pows <- c(p_pows, ps)
    diff_pows <- c(diff_pows, rep((abs(curve_parms[i,4]-curve_parms[i,5])), times=10))

  }
}

# Histogram of p-values
hist(unlist(p_pows), col=3, breaks=20, xlab="p-values", main=NULL)
```

```{r}
plot(c(diff_vals, diff_pows), c(p_vals, p_pows))
```

@@

>>>>

---
title: Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model
author: "Rachael Aber"
header-includes: \usepackage{setspace}\doublespacing
output:
  pdf_document: default
  html_document:
    df_print: paged
geometry: margin=2.54cm
fontsize: 12pt
---

@@

For this project, we use county-level COVID-19 incidence data. Source: [USAFacts](https://usafacts.org/visualizations/coronavirus-covid-19-spread-map/). The data is weekly case counts for each US county.

Approximately one month of data on either side of November 26th, 2020 was used in the analysis. This step was done to include a set number of "waves" of incidence in the model fit to each side of the hypothesized change. However, we acknowledge that there is a trade-off between including few waves and increasing the power of the proposed test by including more time series data.

@@

```{r}
library(knitr)
rat <- data.frame(Mean = c(5, 10), Ratio = c(2.236068, 3.162278))
kable(rat, align = "cc", caption = "Poisson mean to standard deviation ratio", digits=2)
```

@@

```{r, fig.cap="Average Pothoff-Whittinghill (PW) statistic for each NY county plotted against county population size."}
library(tidyverse)
library(changepoint)
source("code/functions_intro.R")

@@

ch_pts <- map(scaled_cases, ~ cpts(cpt.mean(., class = TRUE, penalty = "MBIC", pen.value = 0, method = "PELT", param.estimates = TRUE)))

segments <- map2(.x = as.data.frame(t(new_cases_subset[which(sapply(ch_pts, length) != 0),])), .y = ch_pts[which(sapply(ch_pts, length) != 0)], ~ get_segments(series = .x, changepoints = .y))

@@

plot(populations$population[which(sapply(ch_pts, length) != 0)], log(unlist(mean_pw)), xlab="Log Population Size", ylab=" Log Mean PW Statistic", col=2, xlim=c(0,1000000))
```
Methods designed specifically for count data show a similar dependence on population size. The cpt.meanvar function (changepoint package) is designed to detect changes in mean and variance in count data. The number of changepoints identified for a time series increases with its population size.

@@

ch_pts2 <- map(as.data.frame(t(new_cases_subset)), ~ cpts(cpt.meanvar(., class = TRUE, penalty = "MBIC", pen.value = 30, method = "PELT", test.stat = "Poisson", param.estimates = TRUE, minseglen = 2)))

n_ch_pts2 <- map(ch_pts2, ~length(unlist(.)))

plot(populations$population, log(unlist(n_ch_pts2)), xlab="Log Population Size", ylab=" Log Number of Changepoints", col=2)
```
## Modeling proccess mean

We propose a generalized linear model (GLM) approach to quantify incidence dispersion in segments of a time series, using a single parameter, $\theta$, while separately accounting for population size in the model. Here we account for unobserved heterogeneity, and time dependence in rate - potentially due to contagion - (Barron 1992) by specifying an overdispersed conditional distribution.

A recently proposed negative binomial regression model for time series of counts also accommodates serial dependence (Davis and Wu 2009). The approach presented here is similar, but we use a linear predictor, $\eta$, that includes a natural spline in time. Natural splines are cubic splines which are linear outside of the boundary knots (Perperoglou et al. 2019).

  $$g(E[Y_i]/n_i) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$ $$log(E[Y_i]/n_i) = \sum_m^M\beta_m h_m(t_i)$$
  ,where $n_i$ is the population size, $Y_i$ is incidence, and $t_i$ is the time point.

In this case, we use a log link function:
$$log(E[Y_i]/n_i) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$
  $$log(E[Y_i])-log(n_i) = \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i)$$
  $$log(E[Y_i]) = \beta_1(h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i) + log(n_i)$$
## IRLS

Iteratively reweighted least squares (IRLS) is used to obtain parameter estimates of the model. Briefly, IRLS works by computing an adjusted dependent variable, computing a weight matrix, and then calculating (using weighted least squares) coefficients estimates of the model used to calculate the linear predictor as well. This procedure is implemented via the irls.nb.1 and functions from the NBPSeq R package (https://CRAN.R-project.org/package=NBPSeq) and from Di et al. (2011).

@@

Note that if the offset model were perfect, the estimated coefficient on log population would be exactly one.

@@

# ```{r}
# disp_stats <- c()
# for (i in 1:dim(new_cases_subset[state_index])[1]){
#   Y <- new_cases_subset[i,]
#   spline_mod.1.pois <- spl_fit_pois(Y = Y, population=ny_fl_df_t$populations[i], inds=1:(length(Y)/2))
#   disp_stats <- c(disp_stats, spline_mod.1.pois$deviance/spline_mod.1.pois$df.residual)
# }
# ```

To identify an appropriate conditional distribution, the value of Poisson model residual deviance (D) divided by its degrees of freedom (df) was used to verify that overdispersion at the time point level is present under this model and found that only a few dispersion statistics were less than or equal to one. Since residual deviance of a model is expected to be asymptotically distributed as $\chi^2_{df}$, where the degrees of freedom are the number of observations minus the number of estimated parameters, an indication that a model may be underestimating dispersion (that the data is inconsistent with the model) is that D/df >> 1.

@@

@@

@@

```{r, fig.cap="Example of empirical increase in dispersion at the hypothesized Thanksgiving 2020 changepoint."}
plot(new_cases_subset[1842,], xaxt="n", ylab="Daily Incidence", xlab="Date") #~ inds
abline(v=30, col=2)
#axis(1, inds, inds, cex.axis = .7)
```

We tested the hypothesis that the incidence dispersion parameter decreases at the Thanksgiving changepoint of interest: $\theta_1 > \theta_2$. Hypothesis tests were conducted to assess whether $\theta$ is smaller (more variable incidence) after Thanksgiving 2020. The Wald test is used, where the estimates of $\theta$ in different segments are considered independent. This approach is possible because we use IRLS estimates of $\theta$ - the standard error of $\theta$ is found utilizing the observed information.

@@

## Thanksgiving 2020: Wald test

First, for every county, the model was fit separately to either side of November 26th, 2020 in order to compute values of $\hat{\theta_1}$ and $\hat{\theta_2}$. A test of the one-sided upper alternative that the difference between before and after is positive (lower theta after Thanksgiving) was performed.

```{r, fig.cap = "P-values resulting from testing whether the dispersion parameter is smaller after Thanksgiving in each county in New York (Wald)"}
source("code/wald_counties.R")
```
```{r, fig.cap = "P-values resulting from testing whether the dispersion parameter is smaller after Thanksgiving in each county in New York (LRT)"}
source("code/LRT_counties.R")
```

# Simulation

## Validity and power of the Wald test

@@

```{r, fig.cap="Wald simulation p-values."}
source("code/validity_and_power_Wald.R")
```

@@

@@

## Validity and power of the LRT

```{r, fig.cap="Wald simulation p-values."}
source("code/validity_and_power_LRT.R")
```
